### 2020-06-02 writeup/setup.tex

\section{A Sharp Analysis of the Tradeoff for Multi-Task and Transfer Learning}
\label{sec_main}

@@

\subsection{The Bias-Variance Tradeoff}\label{sec_setup}

@@

\subsection{Applying Theorem \ref{thm_main_informal} to Analyze the Bias-Variance Tradeoff}
%\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}

@@

@@

Theorem \ref{thm_main_informal} shows that as the source task data size increases, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
%determined by the covariate shift matrix and the model shift.
%The bounds get tighter and tighter as $\rho_1$ increases.
While the general form of the threshold can be complex (as is preivous generalization bounds for MTL), they admit interpretable forms for simplified settings.
This will be the focus of Section \ref{sec_insight}.
The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
The result for more than two tasks is deferred to Appendix \ref{app_proof_many_tasks}.

>>>>

\section{Multi-Task vs. Single-Task Learning: The Bias-Variance Tradeoff}
\label{sec_main}

@@

\subsection{Problem Setup}\label{sec_setup}

@@

\subsection{Analyzing the Tradeoff via Random Matrix Theory}

@@

%\subsection{A Key Lemma using Random Matrix Theory}\label{label_rmt}

@@

Theorem \ref{thm_main_informal} shows that as the source task data size increases, we obtain a sharp transition from positive transfer to negative transfer determined by $\Delta_{\bias} - \Delta_{\vari}$.
%determined by the covariate shift matrix and the model shift.
%The bounds get tighter and tighter as $\rho_1$ increases.
While the general form of the threshold can be complex (as is preivous generalization bounds for MTL), they admit interpretable forms for simplified settings.
This will be the focus of Section \ref{sec_insight}.

\textbf{Proof Overview.}
The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
The result for more than two tasks is deferred to Appendix \ref{app_proof_many_tasks}.
